Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
add before and after for private class

Stainless can not extract the private class inside the object.
Bitcoin-S uses this a lot, because they separate the class from its implementation.
Simplified:
\begin{lstlisting}[style=scala]
  object Int64 extends BaseNumbers[Int64] {
    private case class Int64Impl(underlying: BigInt) extends Int64 
  }
\end{lstlisting}

>>>>

Stainless can not extract the private class inside the object.
Bitcoin-S uses this a lot, because they separate the class from its implementation.

Before:
\begin{lstlisting}[style=scala]
case object Satoshis extends BaseNumbers[Satoshis] {
  val min = Satoshis(Int64.min)
  val max = Satoshis(Int64.max)
  val zero = Satoshis(Int64.zero)
  val one = Satoshis(Int64.one)

  def apply(int64: Int64): Satoshis = SatoshisImpl(int64)

  private case class SatoshisImpl(underlying: Int64) extends Satoshis
}
\end{lstlisting}

After:
\begin{lstlisting}[style=scala]
case object Satoshis extends BaseNumbers[Satoshis] {

  val min = Satoshis(Int64.min)
  val max = Satoshis(Int64.max)
  val zero = Satoshis(Int64.zero)
  val one = Satoshis(Int64.one)

  def apply(int64: Int64): Satoshis = SatoshisImpl(int64)
}

private case class SatoshisImpl(underlying: Int64) extends Satoshis
\end{lstlisting}
